Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-23 article.tex
EOD

One important assumption for such phylogenetic inference
is the amino acid substitution model (AASM), which may be different
in TMHs. An AASM encodes the relative rates at which amino acids
change through evolutionary time. Some amino acids have more 
DNA triplets encoding for them, which is reflected in the AASM.
Already for decades, AASMs are devised and refined from whole proteomes,
such as the Blosum62 (\cite{henikoff1992amino}), 
Dayhoff (\cite{dayhoff197822}), JTT (\cite{jones1992rapid}), 
and WAG (\cite{whelan2001general}) models. 
That such a generalization
is not always desired, AASMs are devised for 
chloroplasts (the CPREV model, see \cite{adachi2000plastid})
and mitochondria (the MTREV24 model, see \cite{adachi1996model}).
In all AASM, TMHs are generalized out and therefore, 
there is no specialized AASM for TMHS. It would, however,
be possible to derive an AASM from in silico predictions. 
An in silico prediction would bypass any effects of evolution.
Another AASM could be constructed from humans, if we assume
that there is no selection on TMHs, except for being functional.

@@

>>>>

One important assumption for such phylogenetic inference
is the amino acid substitution model (AASM), which may be different
in TMHs. An AASM encodes the relative rates at which amino acids
change through evolutionary time. Some amino acids have more 
DNA triplets encoding for them, which is reflected in the AASM.
Already for decades, AASMs are devised and refined from whole proteomes,
such as the Blosum62 (\cite{henikoff1992amino}), 
Dayhoff (\cite{dayhoff197822}), JTT (\cite{jones1992rapid}), 
and WAG (\cite{whelan2001general}) models. 
That such a generalization
is not always desired, AASMs are divised for 
chloroplasts (the CPREV model, see \cite{adachi2000plastid})
and mitochondria (the MTREV24 model, see \cite{adachi1996model}).
In all AASM, TMHs are generalized out and therefore, 
there is no specialized AASM for TMHS. It would, however,
be possible to derive an AASM from in silico predictions. 
An in silico prediction would bypass any effects of evolution.
Another AASM could be constructed from humans, if we assume
that there is no selection on TMHs, except for being functional.

@@

\end{document}
new research. 
      This table be deleted in the future.
    }
  }
  \label{table:mhc2_haplotypes}
\end{table}
